Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum: \\A Revised Study of PAPER-64

### 2018-09-10 PAPER.tex
all new plots compiled in paper

Optimistically, we expect there to be a ``sweet spot" as we dial our regularization knob; a level of regularization where weighting 
is beneficial compared to uniform weighting (blue). In other words, we would like a weighting scheme that down-weights eigenmodes that predominantly describe foreground modes, but not EoR modes. We see in Figure \ref{fig:sigloss_modeloop} that this occurs roughly when 
only the $\sim2$-$3$ highest-valued eigenmodes are down-weighted and the rest are given equal weights (though for the case shown, weighting does not actually outperform uniform weighting). For a similar discussion on projecting out modes (zeroing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.

@@

In addition to our thermal noise prediction (green) and uniform-weighted power spectrum limit (blue), one additional horizontal line is shown in Figure \ref{fig:sigloss_modeloop} 
in both panels and represents a third regularization technique. This line (black) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity 
matrix element-wise to $\widehat{\textbf{C}}$). This result is single-valued and not a function of the horizontal axis. We see that all three regularization schemes shown (solid red top panel, solid red bottom panel, black) perform similarly at 
their best (i.e., when $\sim2$-$3$ eigenmodes are down-weighted in the case of the top panel's solid red curve). However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} + 0.09 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.09$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$. We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, noting that the power spectrum upper limit remains roughly constant for a broad range of values of $\gamma$.

>>>>

Optimistically, we expect there to be a ``sweet spot" as we dial our regularization knob; a level of regularization where weighting 
is beneficial compared to uniform weighting (blue). In other words, we would like a weighting scheme that down-weights eigenmodes that predominantly describe foreground modes, but not EoR modes. We see in Figure \ref{fig:sigloss_modeloop} that this occurs roughly when 
only the $\sim3$ highest-valued eigenmodes are down-weighted and the rest are given equal weights (though for the case shown, weighting only slightly outperforms uniform weighting). For a similar discussion on projecting out modes (zeroing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.

@@

In addition to our thermal noise prediction (green) and uniform-weighted power spectrum limit (blue), one additional horizontal line is shown in Figure \ref{fig:sigloss_modeloop} 
in both panels and represents a third regularization technique. This line (black) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity 
matrix element-wise to $\widehat{\textbf{C}}$). This result is single-valued and not a function of the horizontal axis. We see that all three regularization schemes shown (solid red top panel, solid red bottom panel, black) perform similarly at 
their best (i.e., when $\sim3$ eigenmodes are down-weighted in the case of the top panel's solid red curve). However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} + 0.09 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.09$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$. We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, noting that the power spectrum upper limit remains roughly constant for a broad range of values of $\gamma$.
